### 2019-08-07 manuscript_clean.Rmd
wrote discussion chunk and added bibs for VCV analysis

>>>>

  Our evolutionary rate covariance results indicate that tentilla are not only phenotypically integrated, but also show patterns of evolutionary modularity, where different sets of characters appear to evolve in stronger correlations among each other than with other characters. This may be indicative of the underlying genetic and developmental dependencies of homologous nematocyst types (desmonemes and rhopalonemes) and structures. In addition, these evolutionary modules point to hypothetical functional modules. For example, the coiling degree of the cnidoband and the extent of the involucrum have correlated rates of evolution, while high speed videos show that the involucrum helps direct the whiplash of the uncoiling cnidoband forward (towards the prey).

  While selection acting on character states is a widely studied phenomenon, recent studies have shown that selection can also act upon the patterns of character correlations and phenotypic dependencies [@young2005serial;@goswami2006morphological;@revell2009phylogenetic;@monteiro2010adaptive;@hallgrimsson2012generation;@claverie2013modularity;@caetano2018estimating]. This evolution of character relationships can allow lineages to explore new regions of the morphospace and facilitate the appearance of ecological novelties. Our results show that the patterns of phenotypic integration in siphonophore tentilla vary among clades, and appear to display different relationships across shifting feeding specializations. Similarly to what has been found in the feeding morphologies of fish (Collar 2005, Collar Revell 2009), siphonophore tentilla may have accommodated new diets by altering the correlations between characters. For example, changes in the size and shape relationships between nematocyst types gave rise to the nematocyst complements specialized in ensnaring small crustaceans or fish. The evolvability of phenotypic dependencies likely had a large role in the evolution of the diverse tentilla morphologies we observe today in siphonophores.
